A Comparison of Graph Processing Systems

### 2020-09-06 documentation/paper/sections/results/galoisSpeedup.tex
galois speedup bfs updated

For our speedup results on BFS, \autoref{fig:galoisSpeedupBFS} shows the calculation time speedup of Galois' BFS.

Flickr is sped up by about 5\%\ with 4 threads, any more than that will actually decrease performance, making computation time up to 15\%\ (96 threads) longer.

On all graphs, the speedup never exceeds 6$\times$ even when using 96 threads.
The initial speedup when switching from one to two threads is actually smaller than one, thus decreasing performance, on 4 of 7 graphs. Only flickr, twitter and rMat28 can benefit slightly by a speedup of 2\%, 41\%\ and 5\%\ respectively.

When comparing four threads to one, BFS on all but two graphs can be sped up by anywhere from 5\%\ (flickr) to 68\% (rMat28). The speedup is thus only possible to a very small degree.
For the other two graphs, computation on friendster with 8 threads is just as fast as one thread and computation on rMat27 is actually 19\% slower.

\subsubsection{PageRank}
We want to first take a look at the results for PageRank in Pull mode, seen in \autoref{fig:galoisSpeedupPRPull}. This is a perfect example for an algorithm that does not benefit from multithreaded computation. 
Computation is hardly sped up on any graph other than flicker, where the reached maximum is 64\%. This maximum is reached at two threads, with speedup steadily declining above that.
The rMat28 is the only other graph of one could say computation was sped up. Here we reached a maximum speedup of 31\%\ at 96 threads.
All 5 other graphs only reach a speedup greater or equal to 1 in just one or two cases and if so only by a small margin.
Computation on Orkut and Twitter reaches a speedup maximum of 12\%\ and 5\%\ at 4 threads, while being less or equal to 1 in all other cases.
The wikipedia graph is never sped up.
Friendster and rMat27 can be sped up by 6.5\%\ or 10\%\ respectively on 8 threads.

>>>>

For our speedup results on BFS, \autoref{fig:galoisSpeedupBFS} shows the calculation time speedup of Galois' BFS.
On all graphs, the speedup never exceeds 6$\times$ even when using 96 threads.
For the smaller graphs (flickr, orkut), we have the same behaviour as on SSSP. Speedup is close to 1 in all cases, with orkut reaching a maximum speedup of 1.6$\times$ at 24 threads.
On the larger graphs, speedup is possible but only to a very small degree.
Wikipedia has a maximum speedup of 4.9$\times$ at 96 threads, for twitter it is 2.5$\times$ at 96 threads and 5.6$\times$ on friendster. The two synthetic data sets reach speedups of 4.2$\times$ and 4.7$\times$ for rMat27 and rMat28 on 96 threads.

\subsubsection{PageRank}
We want to first take a look at the results for PageRank in Pull mode, seen in \autoref{fig:galoisSpeedupPRPull}. This is a perfect example for an algorithm that does not benefit from multithreaded computation. 
Computation is hardly sped up on any graph other than flicker, where the reached maximum is 64\%. This maximum is reached at two threads, with speedup steadily declining above that.
The rMat28 is the only other graph of one could say computation was sped up at large thread counts. Here we reached a maximum speedup of 31\%\ at 96 threads.
All 5 other graphs only reach a speedup greater or equal to 1 in just one or two cases and if so only by a small margin.
Computation on Orkut and Twitter reaches a speedup maximum of 12\%\ and 5\%\ at 4 threads, while being less or equal to 1 in all other cases.
The wikipedia graph is never sped up.
Friendster and rMat27 can be sped up by 6.5\%\ or 10\%\ respectively on 8 threads.
